A Roadmap for\\HEP Software and Computing R\&D\\for the 2020s

### 2017-12-18 CWP/papers/roadmap/latex/authors.tex
Updated author list for 2017-12-18
- Generated from Google Doc on 2107-12-18T1300
- Add also a saved copy of the arXiv author metadata
Fix encoding problem with text files not being in utf-8
Fix white space issues and remove duplicate Oslo entry
Update key for SaoPaulo (minor)
Resulting authors.tex file copied to LaTeX area for roadmap

Alves Jr, Antonio Augusto $^{74}$;
Amadio, Guilherme $^{5}$;
Anh-Ky, Nguyen $^{111}$;
Aphecetche, Laurent $^{60}$;
Apostolakis, John $^{5}$;
Asai, Makoto $^{58,p}$;
Atzori, Luca $^{5}$;
Babik, Marian $^{5}$;
Bagliesi, Giuseppe $^{29}$;
Bandieramonte, Marilena $^{5}$;
Barisits, Martin $^{5}$;
Bauerdick, Lothar A. T. $^{16,c}$;
Belforte, Stefano $^{32}$;
Benjamin, Douglas $^{75}$;
Bernius, Catrin $^{58}$;
Bhimji, Wahid $^{42}$;
Bianchi, Riccardo Maria $^{97}$;
Bird, Ian $^{5}$;
Biscarat, Catherine $^{48}$;
Blomer, Jakob $^{5}$;
Bloom, Kenneth $^{89}$;
Boccali, Tommaso $^{29}$;
Bockelman, Brian $^{89}$;
Bold, Tomasz $^{39}$;
Bonacorsi, Daniele $^{24}$;
Boveia, Antonio $^{94}$;
Bozzi, Concezio $^{26}$;
Bracko, Marko $^{86,37}$;
Britton, David $^{79}$;
Buckley, Andy $^{79}$;
Buncic, Predrag $^{5,a}$;
Calafiura, Paolo $^{42}$;
Campana, Simone $^{5,a}$;
Canal, Philippe $^{16,c}$;
Canali, Luca $^{5}$;
Carlino, Gianpaolo $^{28}$;
Castro, Nuno $^{43,88,d}$;
Cattaneo, Marco $^{5}$;
Cerminara, Gianluca $^{5}$;
Chang, Philip $^{69}$;
Chapman, John $^{70}$;
Childers, Taylor $^{1}$;
Clarke, Peter $^{76}$;
Clemencic, Marco $^{5}$;
Cogneras, Eric $^{46}$;
Collier, Ian $^{56}$;
Corti, Gloria $^{5}$;
Cosmo, Gabriele $^{5}$;
Costanzo, Davide $^{103}$;
Couturier, Ben $^{5}$;
Cranmer, Kyle $^{53}$;
Cranshaw, Jack $^{1}$;
Crépé-Renaudin, Sabine $^{48}$;
Cristella, Leonardo $^{25}$;
Crooks, David $^{79}$;
Dallmeier-Tiessen, Sünje $^{5}$;
De Cian, Michel $^{80}$;
De, Kaushik $^{105}$;
Di Girolamo, Alessandro $^{5}$;
Dimitrov, Gancho $^{5}$;
Doglioni, Caterina $^{84,h}$;
Dotti, Andrea $^{58,p}$;
Duellmann, Dirk $^{5}$;
Duflot, Laurent $^{41}$;
Dykstra, Dave $^{16,c}$;
Dziedziniewicz-Wojcik, Katarzyna $^{5}$;
Dziurda, Agnieszka $^{5}$;
Egede, Ulrik $^{34}$;
Elmer, Peter $^{98,a}$;
Elmsheuser, Johannes $^{2}$;
Elvira, V. Daniel $^{16,c}$;
Eulisse, Giulio $^{5}$;
Ferber, Torben $^{67}$;
Filipcic, Andrej $^{37}$;
Fisk, Ian $^{59}$;
Fitzpatrick, Conor $^{14}$;
Flix, José $^{55,7,g}$;
Formica, Andrea $^{35}$;
Forti, Alessandra $^{85}$;
Gaede, Frank $^{13}$;
Ganis, Gerardo $^{5}$;
Gardner, Robert $^{73}$;
Garonne, Vincent $^{95}$;
Gellrich, Andreas $^{13}$;
Genser, Krzysztof $^{16,c}$;
George, Simon $^{57}$;
Geurts, Frank $^{99}$;
Gheata, Andrei $^{5}$;
Gheata, Mihaela $^{5}$;
Giacomini, Francesco $^{9}$;
Giagu, Stefano $^{101,31}$;
Giffels, Manuel $^{38}$;
Gingrich, Douglas $^{63}$;
Girone, Maria $^{5}$;
Gligorov, Vladimir V. $^{47}$;
Glushkov, Ivan $^{105}$;
Gohn, Wesley $^{81}$;
González Caballero, Isidro $^{96}$;
González Fernández, Juan R. $^{96}$;
Gonzalez Lopez, Jose Benito $^{5}$;
Govi, Giacomo $^{16}$;
Grandi, Claudio $^{24}$;
Grasland, Hadrien $^{41}$;
Gray, Heather $^{42}$;
Grillo, Lucia $^{85}$;
Guan, Wen $^{109}$;
Gutsche, Oliver $^{16,c}$;
Gyurjyan, Vardan $^{36}$;
Hanushevsky, Andrew $^{58,p}$;
Hariri, Farah $^{5}$;
Hartmann, Thomas $^{13}$;
Harvey, John $^{5,a}$;
Hauth, Thomas $^{38}$;
Hegner, Benedikt $^{5,a}$;
Heinemann, Beate $^{13}$;
Heinrich, Lukas $^{53}$;
Hernández, José M. $^{7,g}$;
Hildreth, Michael $^{91,f}$;
Hodgkinson, Mark $^{103}$;
Hoeche, Stefan $^{58,p}$;
Hristov, Peter $^{5}$;
Huang, Xingtao $^{102}$;
Ivanchenko, Vladimir N. $^{5,106}$;
Ivanov, Todor $^{104}$;
Jashal, Brij $^{62}$;
Jayatilaka, Bodhitha $^{16,c}$;
Jones, Roger $^{82,a}$;
Jouvin, Michel $^{41,a}$;
Jun, Soon Yung $^{16,c}$;
Kagan, Michael $^{58,p}$;
Kalderon, Charles William $^{84}$;
Karavakis, Edward $^{5}$;
Katz, Daniel S. $^{72}$;
Kcira, Dorian $^{11}$;
Kersevan, Borut Paul $^{83}$;
Kirby, Michael $^{16,c}$;
Klimentov, Alexei $^{2}$;
Klute, Markus $^{49}$;
Komarov, Ilya $^{32,n}$;
Koppenburg, Patrick $^{52}$;
Kowalkowski, Jim $^{16,c}$;
Kreczko, Luke $^{66}$;
Kuhr, Thomas $^{45,a}$;
Kutschke, Robert $^{16,a,c}$;
Kuznetsov, Valentin $^{12}$;
Lampl, Walter $^{65}$;
Lancon, Eric $^{2}$;
Lange, David $^{98}$;
Lassnig, Mario $^{5}$;
Laycock, Paul $^{5}$;
Leggett, Charles $^{42}$;
Letts, James $^{69}$;
Lewendel, Birgit $^{13}$;
Li, Teng $^{76}$;
Lima, Guilherme $^{16}$;
Linacre, Jacob $^{56,m}$;
Linden, Tomas $^{18}$;
Lo Presti, Giuseppe $^{5}$;
Lopienski, Sebastian $^{5}$;
Love, Peter $^{82}$;
Marshall, Zachary L $^{42}$;
Martelli, Edoardo $^{5}$;
Martin-Haugh, Stewart $^{56}$;
Mato, Pere $^{5}$;
Mazumdar, Kajari $^{62}$;
McCauley, Thomas $^{91}$;
McFayden, Josh $^{5}$;
McKee, Shawn $^{87,l}$;
McNab, Andrew $^{85}$;
Meinhard, Helge $^{5}$;
Menasce, Dario $^{27,a}$;
Mendez Lorenzo, Patricia $^{5}$;
Mete, Alaettin Serhan $^{68}$;
Michelotto, Michele $^{30}$;
Mitrevski, Jovan $^{45}$;
Moneta, Lorenzo $^{5}$;
Morgan, Ben $^{108}$;
Mount, Richard $^{58,p}$;
Moyse, Edward $^{64}$;
Murray, Sean $^{71,10}$;
Neubauer, Mark S $^{72,a,k}$;
Novaes, Sérgio $^{100}$;
Novak, Mihaly $^{5}$;
Oyanguren, Arantza $^{21}$;
Ozturk, Nurcan $^{105}$;
Pacheco Pages, Andres $^{55,19,j}$;
Paganini, Michela $^{110}$;
Pansanel, Jerome $^{33}$;
Pascuzzi, Vincent R. $^{107}$;
Pearce, Alex $^{5}$;
Pearson, Ben $^{50}$;
Pedro, Kevin $^{16,c}$;
Perdue, Gabriel $^{16}$;
Perez-Calero Yzquierdo, Antonio $^{55,7,g}$;
Perrozzi, Luca $^{15}$;
Petersen, Troels $^{51}$;
Petric, Marko $^{5}$;
Piedra, Jónatan $^{20}$;
Piilonen, Leo $^{112,i}$;
Piparo, Danilo $^{5}$;
Pokorski, Witold $^{5}$;
Polci, Francesco $^{47}$;
Potamianos, Karolos $^{13}$;
Psihas, Fernanda $^{23}$;
Raven, Gerhard $^{52}$;
Reuter, Jürgen $^{13}$;
Ribon, Alberto $^{5}$;
Ritter, Martin $^{45}$;
Robinson, James $^{13}$;
Rodrigues, Eduardo $^{74,a,e}$;
Roiser, Stefan $^{5,a}$;
Rousseau, David $^{41}$;
Roy, Gareth $^{79}$;
Sailer, Andre $^{5}$;
Sakuma, Tai $^{66}$;
Sánchez-Hernández, Alberto $^{8,o}$;
Santana, Renato $^{3}$;
Sartirana, Andrea $^{44}$;
Schellman, Heidi $^{54}$;
Schovancová, Jaroslava $^{5}$;
Schramm, Steven $^{78}$;
Schulz, Markus $^{5}$;
Sciabà, Andrea $^{5}$;
Seidel, Sally $^{90}$;
Sekmen, Sezen $^{40}$;
Serfon, Cedric $^{93}$;
Severini, Horst $^{92}$;
Sexton-Kennedy, Elizabeth $^{16,a,c}$;
Seymour, Michael $^{85}$;
Shapoval, Illya $^{42}$;
Shiers, Jamie $^{5}$;
Shiu, Jing-Ge $^{61}$;
Short, Hannah $^{5}$;
Siroli, Gian Piero $^{24}$;
Skipsey, Sam $^{79}$;
Smith, Tim $^{5}$;
Snyder, Scott $^{2}$;
Sokoloff, Michael D $^{74,a}$;
Stadie, Hartmut $^{17}$;
Stark, Giordon $^{6}$;
Stewart, Gordon $^{79}$;
Stewart, Graeme $^{5,a}$;
Templon, Jeff $^{52}$;
Tenaglia, Giacomo $^{5}$;
Tsulaia, Vakhtang $^{42}$;
Tunnell, Christopher $^{6}$;
Vaandering, Eric $^{16,c}$;
Valassi, Andrea $^{5}$;
Vallecorsa, Sofia $^{77}$;
Valsan, Liviu $^{5}$;
Van Gemmeren, Peter $^{1}$;
Vázquez Sierra, Carlos $^{52}$;
Vernet, Renaud $^{4}$;
Viren, Brett $^{2}$;
Vlimant, Jean-Roch $^{11,a}$;
Voss, Christian $^{13}$;
Vuosalo, Carl $^{113}$;
Wartel, Romain $^{5}$;
Wenaus, Torre $^{2}$;
Wenzel, Sandro $^{5}$;
Winklmeier, Frank $^{54}$;
Wissing, Christoph $^{13}$;
Wuerthwein, Frank $^{69}$;
Wynne, Benjamin $^{76}$;
Xiaomei, Zhang $^{22}$;
Yang, Wei $^{58,p}$;
Yazgan, Efe $^{22}$

@@

\par {\footnotesize $^{3}$ Centro Brasileiro de Pesquisas Fisicas, Rio de Janeiro, Brazil}

@@

\par {\footnotesize $^{14}$ Institute of Physics, Ecole Polytechnique Federale de Lausanne (EPFL), Lausanne, Switzerland}

@@

\par {\footnotesize $^{21}$ Instituto de Fisica Corpuscular, Centro Mixto Universidad de Valencia - CSIC, Valencia, Spain}

@@

\par {\footnotesize $^{26}$ Universita e INFN, Ferrara, Ferrara, Italy}

@@

\par {\footnotesize $^{35}$ DSM/IRFU (Institut de Recherches sur les Lois Fondamentales de l’Univers), CEA Saclay (Commissariat a l’Energie Atomique), Gif-sur-Yvette, France}

@@

\par {\footnotesize $^{37}$ Jozef Stefan Institute, Ljubljana, Slovenia}

@@

\par {\footnotesize $^{43}$ Laboratorio de Instrumentacao e Fisica Experimental de Particulas (LIP), Lisboa, Portugal}
\par {\footnotesize $^{44}$ Laboratoire Leprince-Ringuet, Ecole polytechnique, CNRS/IN2P3, Université Paris-Saclay, Palaiseau, France}

@@

\par {\footnotesize $^{47}$ LPNHE, Universite Pierre et Marie Curie, Universite Paris Diderot, CNRS/IN2P3, Paris, France}

@@

\par {\footnotesize $^{81}$ Department of Physics \& Astronomy, University of Kentucky, Lexington, USA}

@@

\par {\footnotesize $^{84}$ Fysiska institutionen, Lunds universitet, Lund, Sweden}

@@

\par {\footnotesize $^{88}$ Departamento de Fisica, Universidade de Minho, Braga, Portugal}

@@

\par {\footnotesize $^{93}$ Department of Physics, University of Oslo, Oslo, Norway}
\par {\footnotesize $^{94}$ The Ohio State University, Columbus, USA}
\par {\footnotesize $^{95}$ Department of Physics, University of Oslo, Oslo, Norway}
\par {\footnotesize $^{96}$ Universidad de Oviedo, Oviedo, Spain}
\par {\footnotesize $^{97}$ Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, PA, USA}
\par {\footnotesize $^{98}$ Princeton University, Princeton, USA}
\par {\footnotesize $^{99}$ Rice University, Houston, USA}
\par {\footnotesize $^{100}$ Universidade Estadual Paulista, São Paulo, Brazil}
\par {\footnotesize $^{101}$ Dipartimento di Fisica, Università La Sapienza, Roma, Italy}
\par {\footnotesize $^{102}$ School of Physics, Shandong University, Shandong, China}
\par {\footnotesize $^{103}$ Department of Physics and Astronomy, University of Sheffield, Sheffield, United Kingdom}
\par {\footnotesize $^{104}$ University of Sofia, Sofia, Bulgaria}
\par {\footnotesize $^{105}$ Department of Physics, The University of Texas at Arlington, Arlington, TX, USA}
\par {\footnotesize $^{106}$ National Research Tomsk Polytechnic University, Tomsk, Russia}
\par {\footnotesize $^{107}$ Department of Physics, University of Toronto, Toronto, ON, Canada}
\par {\footnotesize $^{108}$ Department of Physics, University of Warwick, Coventry, United Kingdom}
\par {\footnotesize $^{109}$ University ofWisconsin - Madison, Madison, WI, USA}
\par {\footnotesize $^{110}$ Department of Physics, Yale University, New Haven, CT, USA}
\par {\footnotesize $^{111}$ IOP and GUST, Vietnam Academy of Science and Technology (VAST), Hanoi, Vietnam}
\par {\footnotesize $^{112}$ Virginia Tech, Blacksburg, Virginia, USA}
\par {\footnotesize $^{113}$ Department of Physics, University of Wisconsin, Madison WI, USA}

@@

\par {\footnotesize $^{b}$ Vladimir V. Gligorov acknowledges funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme under grant agreement No 724777 “RECEPT”.}

@@

\par {\footnotesize $^{h}$ Caterina Doglioni acknowledges funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme under grant agreement No 679305 “DARKJETS”.}

>>>>

Alves Jr, Antonio Augusto$^{74}$;
Amadio, Guilherme$^{5}$;
Anh-Ky, Nguyen$^{110}$;
Aphecetche, Laurent$^{60}$;
Apostolakis, John$^{5}$;
Asai, Makoto$^{58,p}$;
Atzori, Luca$^{5}$;
Babik, Marian$^{5}$;
Bagliesi, Giuseppe$^{29}$;
Bandieramonte, Marilena$^{5}$;
Barisits, Martin$^{5}$;
Bauerdick, Lothar A. T.$^{16,c}$;
Belforte, Stefano$^{32}$;
Benjamin, Douglas$^{75}$;
Bernius, Catrin$^{58}$;
Bhimji, Wahid$^{42}$;
Bianchi, Riccardo Maria$^{96}$;
Bird, Ian$^{5}$;
Biscarat, Catherine$^{48}$;
Blomer, Jakob$^{5}$;
Bloom, Kenneth$^{89}$;
Boccali, Tommaso$^{29}$;
Bockelman, Brian$^{89}$;
Bold, Tomasz$^{39}$;
Bonacorsi, Daniele$^{24}$;
Boveia, Antonio$^{93}$;
Bozzi, Concezio$^{26}$;
Bracko, Marko$^{86,37}$;
Britton, David$^{79}$;
Buckley, Andy$^{79}$;
Buncic, Predrag$^{5,a}$;
Calafiura, Paolo$^{42}$;
Campana, Simone$^{5,a}$;
Canal, Philippe$^{16,c}$;
Canali, Luca$^{5}$;
Carlino, Gianpaolo$^{28}$;
Castro, Nuno$^{43,88,d}$;
Cattaneo, Marco$^{5}$;
Cerminara, Gianluca$^{5}$;
Chang, Philip$^{69}$;
Chapman, John$^{70}$;
Chen, Gang$^{22}$;
Childers, Taylor$^{1}$;
Clarke, Peter$^{76}$;
Clemencic, Marco$^{5}$;
Cogneras, Eric$^{46}$;
Collier, Ian$^{56}$;
Corti, Gloria$^{5}$;
Cosmo, Gabriele$^{5}$;
Costanzo, Davide$^{102}$;
Couturier, Ben$^{5}$;
Cranmer, Kyle$^{53}$;
Cranshaw, Jack$^{1}$;
Cristella, Leonardo$^{25}$;
Crooks, David$^{79}$;
Crépé-Renaudin, Sabine$^{48}$;
Dallmeier-Tiessen, Sünje$^{5}$;
De, Kaushik$^{104}$;
De Cian, Michel$^{80}$;
Di Girolamo, Alessandro$^{5}$;
Dimitrov, Gancho$^{5}$;
Doglioni, Caterina$^{84,h}$;
Dotti, Andrea$^{58,p}$;
Duellmann, Dirk$^{5}$;
Duflot, Laurent$^{41}$;
Dykstra, Dave$^{16,c}$;
Dziedziniewicz-Wojcik, Katarzyna$^{5}$;
Dziurda, Agnieszka$^{5}$;
Egede, Ulrik$^{34}$;
Elmer, Peter$^{97,a}$;
Elmsheuser, Johannes$^{2}$;
Elvira, V. Daniel$^{16,c}$;
Eulisse, Giulio$^{5}$;
Ferber, Torben$^{67}$;
Filipcic, Andrej$^{37}$;
Fisk, Ian$^{59}$;
Fitzpatrick, Conor$^{14}$;
Flix, José$^{55,7,g}$;
Formica, Andrea$^{35}$;
Forti, Alessandra$^{85}$;
Gaede, Frank$^{13}$;
Ganis, Gerardo$^{5}$;
Gardner, Robert$^{73}$;
Garonne, Vincent$^{94}$;
Gellrich, Andreas$^{13}$;
Genser, Krzysztof$^{16,c}$;
George, Simon$^{57}$;
Geurts, Frank$^{98}$;
Gheata, Andrei$^{5}$;
Gheata, Mihaela$^{5}$;
Giacomini, Francesco$^{9}$;
Giagu, Stefano$^{100,31}$;
Giffels, Manuel$^{38}$;
Gingrich, Douglas$^{63}$;
Girone, Maria$^{5}$;
Gligorov, Vladimir V.$^{47}$;
Glushkov, Ivan$^{104}$;
Gohn, Wesley$^{81}$;
Gonzalez Lopez, Jose Benito$^{5}$;
González Caballero, Isidro$^{95}$;
González Fernández, Juan R.$^{95}$;
Govi, Giacomo$^{16}$;
Grandi, Claudio$^{24}$;
Grasland, Hadrien$^{41}$;
Gray, Heather$^{42}$;
Grillo, Lucia$^{85}$;
Guan, Wen$^{108}$;
Gutsche, Oliver$^{16,c}$;
Gyurjyan, Vardan$^{36}$;
Hanushevsky, Andrew$^{58,p}$;
Hariri, Farah$^{5}$;
Hartmann, Thomas$^{13}$;
Harvey, John$^{5,a}$;
Hauth, Thomas$^{38}$;
Hegner, Benedikt$^{5,a}$;
Heinemann, Beate$^{13}$;
Heinrich, Lukas$^{53}$;
Hernández, José M.$^{7,g}$;
Hildreth, Michael$^{91,f}$;
Hodgkinson, Mark$^{102}$;
Hoeche, Stefan$^{58,p}$;
Hristov, Peter$^{5}$;
Huang, Xingtao$^{101}$;
Ivanchenko, Vladimir N.$^{5,105}$;
Ivanov, Todor$^{103}$;
Jashal, Brij$^{62}$;
Jayatilaka, Bodhitha$^{16,c}$;
Jones, Roger$^{82,a}$;
Jouvin, Michel$^{41,a}$;
Jun, Soon Yung$^{16,c}$;
Kagan, Michael$^{58,p}$;
Kalderon, Charles William$^{84}$;
Karavakis, Edward$^{5}$;
Katz, Daniel S.$^{72}$;
Kcira, Dorian$^{11}$;
Kersevan, Borut Paul$^{83}$;
Kirby, Michael$^{16,c}$;
Klimentov, Alexei$^{2}$;
Klute, Markus$^{49}$;
Komarov, Ilya$^{32,n}$;
Koppenburg, Patrick$^{52}$;
Kowalkowski, Jim$^{16,c}$;
Kreczko, Luke$^{66}$;
Kuhr, Thomas$^{45,a}$;
Kutschke, Robert$^{16,a,c}$;
Kuznetsov, Valentin$^{12}$;
Lampl, Walter$^{65}$;
Lancon, Eric$^{2}$;
Lange, David$^{97}$;
Lassnig, Mario$^{5}$;
Laycock, Paul$^{5}$;
Leggett, Charles$^{42}$;
Letts, James$^{69}$;
Lewendel, Birgit$^{13}$;
Li, Teng$^{76}$;
Lima, Guilherme$^{16}$;
Linacre, Jacob$^{56,m}$;
Linden, Tomas$^{18}$;
Lo Presti, Giuseppe$^{5}$;
Lopienski, Sebastian$^{5}$;
Love, Peter$^{82}$;
Marshall, Zachary L$^{42}$;
Martelli, Edoardo$^{5}$;
Martin-Haugh, Stewart$^{56}$;
Mato, Pere$^{5}$;
Mazumdar, Kajari$^{62}$;
McCauley, Thomas$^{91}$;
McFayden, Josh$^{5}$;
McKee, Shawn$^{87,l}$;
McNab, Andrew$^{85}$;
Meinhard, Helge$^{5}$;
Menasce, Dario$^{27,a}$;
Mendez Lorenzo, Patricia$^{5}$;
Mete, Alaettin Serhan$^{68}$;
Michelotto, Michele$^{30}$;
Mitrevski, Jovan$^{45}$;
Moneta, Lorenzo$^{5}$;
Morgan, Ben$^{107}$;
Mount, Richard$^{58,p}$;
Moyse, Edward$^{64}$;
Murray, Sean$^{71,10}$;
Neubauer, Mark S$^{72,a,k}$;
Novaes, Sérgio$^{99}$;
Novak, Mihaly$^{5}$;
Oyanguren, Arantza$^{21}$;
Ozturk, Nurcan$^{104}$;
Pacheco Pages, Andres$^{55,19,j}$;
Paganini, Michela$^{109}$;
Pansanel, Jerome$^{33}$;
Pascuzzi, Vincent R.$^{106}$;
Pearce, Alex$^{5}$;
Pearson, Ben$^{50}$;
Pedro, Kevin$^{16,c}$;
Perdue, Gabriel$^{16}$;
Perez-Calero Yzquierdo, Antonio$^{55,7,g}$;
Perrozzi, Luca$^{15}$;
Petersen, Troels$^{51}$;
Petric, Marko$^{5}$;
Piedra, Jónatan$^{20}$;
Piilonen, Leo$^{111,i}$;
Piparo, Danilo$^{5}$;
Pokorski, Witold$^{5}$;
Polci, Francesco$^{47}$;
Potamianos, Karolos$^{13}$;
Psihas, Fernanda$^{23}$;
Raven, Gerhard$^{52}$;
Reuter, Jürgen$^{13}$;
Ribon, Alberto$^{5}$;
Ritter, Martin$^{45}$;
Robinson, James$^{13}$;
Rodrigues, Eduardo$^{74,a,e}$;
Roiser, Stefan$^{5,a}$;
Rousseau, David$^{41}$;
Roy, Gareth$^{79}$;
Sailer, Andre$^{5}$;
Sakuma, Tai$^{66}$;
Santana, Renato$^{3}$;
Sartirana, Andrea$^{44}$;
Schellman, Heidi$^{54}$;
Schovancová, Jaroslava$^{5}$;
Schramm, Steven$^{78}$;
Schulz, Markus$^{5}$;
Sciabà, Andrea$^{5}$;
Seidel, Sally$^{90}$;
Sekmen, Sezen$^{40}$;
Serfon, Cedric$^{94}$;
Severini, Horst$^{92}$;
Sexton-Kennedy, Elizabeth$^{16,a,c}$;
Seymour, Michael$^{85}$;
Shapoval, Illya$^{42}$;
Shiers, Jamie$^{5}$;
Shiu, Jing-Ge$^{61}$;
Short, Hannah$^{5}$;
Siroli, Gian Piero$^{24}$;
Skipsey, Sam$^{79}$;
Smith, Tim$^{5}$;
Snyder, Scott$^{2}$;
Sokoloff, Michael D$^{74,a}$;
Stadie, Hartmut$^{17}$;
Stark, Giordon$^{6}$;
Stewart, Gordon$^{79}$;
Stewart, Graeme$^{5,a}$;
Sánchez-Hernández, Alberto$^{8,o}$;
Templon, Jeff$^{52}$;
Tenaglia, Giacomo$^{5}$;
Tsulaia, Vakhtang$^{42}$;
Tunnell, Christopher$^{6}$;
Vaandering, Eric$^{16,c}$;
Valassi, Andrea$^{5}$;
Vallecorsa, Sofia$^{77}$;
Valsan, Liviu$^{5}$;
Van Gemmeren, Peter$^{1}$;
Vernet, Renaud$^{4}$;
Viren, Brett$^{2}$;
Vlimant, Jean-Roch$^{11,a}$;
Voss, Christian$^{13}$;
Vuosalo, Carl$^{108}$;
Vázquez Sierra, Carlos$^{52}$;
Wartel, Romain$^{5}$;
Wenaus, Torre$^{2}$;
Wenzel, Sandro$^{5}$;
Winklmeier, Frank$^{54}$;
Wissing, Christoph$^{13}$;
Wuerthwein, Frank$^{69}$;
Wynne, Benjamin$^{76}$;
Xiaomei, Zhang$^{22}$;
Yang, Wei$^{58,p}$;
Yazgan, Efe$^{22}$

@@

\par {\footnotesize $^{3}$ Centro Brasileiro de Pesquisas Físicas, Rio de Janeiro, Brazil}

@@

\par {\footnotesize $^{14}$ Institute of Physics, École Polytechnique Fédérale de Lausanne (EPFL), Lausanne, Switzerland}

@@

\par {\footnotesize $^{21}$ Instituto de Física Corpuscular, Centro Mixto Universidad de Valencia - CSIC, Valencia, Spain}

@@

\par {\footnotesize $^{26}$ Università e INFN, Ferrara, Ferrara, Italy}

@@

\par {\footnotesize $^{35}$ DSM/IRFU (Institut de Recherches sur les Lois Fondamentales de l’Univers), CEA Saclay (Commissariat à l’Énergie Atomique), Gif-sur-Yvette, France}

@@

\par {\footnotesize $^{37}$ Jožef Stefan Institute, Ljubljana, Slovenia}

@@

\par {\footnotesize $^{43}$ Laboratório de Instrumentação e Física Experimental de Partículas (LIP), Lisboa, Portugal}
\par {\footnotesize $^{44}$ Laboratoire Leprince-Ringuet, École Polytechnique, CNRS/IN2P3, Université Paris-Saclay, Palaiseau, France}

@@

\par {\footnotesize $^{47}$ LPNHE, Université Pierre et Marie Curie, Université Paris Diderot, CNRS/IN2P3, Paris, France}

@@

\par {\footnotesize $^{81}$ Department of Physics and Astronomy, University of Kentucky, Lexington, USA}

@@

\par {\footnotesize $^{84}$ Fysiska institutionen, Lunds Universitet, Lund, Sweden}

@@

\par {\footnotesize $^{88}$ Departamento de Física, Universidade do Minho, Braga, Portugal}

@@

\par {\footnotesize $^{93}$ The Ohio State University, Columbus, USA}
\par {\footnotesize $^{94}$ Department of Physics, University of Oslo, Oslo, Norway}
\par {\footnotesize $^{95}$ Universidad de Oviedo, Oviedo, Spain}
\par {\footnotesize $^{96}$ Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, PA, USA}
\par {\footnotesize $^{97}$ Princeton University, Princeton, USA}
\par {\footnotesize $^{98}$ Rice University, Houston, TX, USA}
\par {\footnotesize $^{99}$ Universidade Estadual Paulista, São Paulo, Brazil}
\par {\footnotesize $^{100}$ Dipartimento di Fisica, Università La Sapienza, Roma, Italy}
\par {\footnotesize $^{101}$ School of Physics, Shandong University, Shandong, China}
\par {\footnotesize $^{102}$ Department of Physics and Astronomy, University of Sheffield, Sheffield, United Kingdom}
\par {\footnotesize $^{103}$ University of Sofia, Sofia, Bulgaria}
\par {\footnotesize $^{104}$ Department of Physics, The University of Texas at Arlington, Arlington, TX, USA}
\par {\footnotesize $^{105}$ National Research Tomsk Polytechnic University, Tomsk, Russia}
\par {\footnotesize $^{106}$ Department of Physics, University of Toronto, Toronto, ON, Canada}
\par {\footnotesize $^{107}$ Department of Physics, University of Warwick, Coventry, United Kingdom}
\par {\footnotesize $^{108}$ University of Wisconsin - Madison, Madison, WI, USA}
\par {\footnotesize $^{109}$ Department of Physics, Yale University, New Haven, CT, USA}
\par {\footnotesize $^{110}$ IOP and GUST, Vietnam Academy of Science and Technology (VAST), Hanoi, Vietnam}
\par {\footnotesize $^{111}$ Virginia Tech, Blacksburg, Virginia, USA}

@@

\par {\footnotesize $^{b}$ Vladimir V. Gligorov acknowledges funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme under grant agreement No 724777 “RECEPT”}

@@

\par {\footnotesize $^{h}$ Caterina Doglioni acknowledges funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme under grant agreement No 679305 “DARKJETS”}
